# Instrumentation and Software {#instrumentation-and-software}


## Instrumentation 

All of the images used in this thesis were acquired on a Leica SP8 confocal microscope^[https://www.leica-microsystems.com/products/confocal-microscopes/details/product/leica-tcs-sp8] equipped with hybrid detectors (section \@ref(HyDs)). Importantly, the detectors that we have on this microscope are capable of photon counting. 



## Software programs, languages and tools


### C++

_C++_ [@cpp] is a genaral-purpose programming language optimized for performance (speed), efficiency (with use of computer resources) and flexibility.^[https://en.wikipedia.org/wiki/C%2B%2B] I used it for its speed, since many of the algorithms that I developed were quite computationally intensive and hence speed was an important consideration.


### R 

_R_ [@R] is a programming language and free software environment for statistical computing and graphics.^[https://en.wikipedia.org/wiki/R_(programming_language)] I use R primarily as a wrapper for my C++ code to make my algorithms more user-friendly. R is best used with the _RStudio_ integrated development environment.^[https://www.rstudio.com]


### ImageJ

_ImageJ_ [ImageJ] is an open source image processing program designed for scientific multidimensional images.^[https://imagej.net] It is the preferred image viewing and analysis software in the community. I have written my software in C++ and R because they are easier for developers, but I still intend to translate my image-related algorithms ImageJ plugins. ImageJ is best used via the FIJI [@FIJI] distribution.^[https://imagej.net/Fiji]


### Git and GitHub

Git is a free and open source distributed version control system designed to handle everything from small to very large projects with speed and efficiency.^[https://git-scm.com/] GitHub is a web-based hosting service for version control using Git.^[https://en.wikipedia.org/wiki/GitHub] All of the computer code used during my thesis can be found on my GitHub at https://github.com/rorynolan. The vast majority of my time during my thesis was spent writing code so this GitHub account is the best record of the work that I have done.



## My software packages


### `ijtiff`

```{r ijtiff-downloads, echo=FALSE}

get_downloads <- function(pkg) {
  pd_path <- here("misc", "package-downloads.csv")
  if (has_internet()) {
    since2010 <- cran_downloads(pkg, from = "2010-01-01", 
                              to = as.character(today()))
    first_nonzero_count <- match(T, since2010$count > 0)
    since2010 %<>% {.[seq_len(nrow(.)) >= first_nonzero_count, ]}
    n_days <- nrow(since2010)
    out <- tibble(package = pkg, 
                  total = sum(since2010$count), 
                  per_month = round(total / n_days * 365.25 / 12)) %>% 
      mutate_if(is.numeric, format, scientific = FALSE)
    if (file.exists(pd_path)) {
      new_pd_df <- pd_path %>% 
        read_csv() %>% 
        mutate_if(is.numeric, format, scientific = FALSE) %>% 
        bind_rows(out, .) %>% 
        filter(!duplicated(package)) %>% 
        write_csv(pd_path)
    } else {
      write_csv(out, pd_path)
    }
  }
  suppressMessages(read_csv(pd_path)) %>% 
    filter(package == pkg) %>% 
    mutate_if(is.numeric, formatC, format = "d", big.mark = ",")
}
ijtiff_downloads <- get_downloads("ijtiff")
```

An R package for general purpose TIFF file I/O. This is currently the only such package with read and write support for TIFF files with floating point (real-numbered) pixels, and the only package that can correctly import TIFF files that were saved from _ImageJ_ [@ImageJ]. R has millions of users worldwide so this TIFF I/O capability is a basic need for masses of people. `ijtiff` gets `r ijtiff_downloads$per_month` downloads per month which amounts to `r ijtiff_downloads$total` since it was first released.

This package is part of the _rOpenSci_ project. rOpenSci is a non-profit initiative founded to make scientific data retrieval reproducible.^[https://ropensci.org/about] This package was peer reviewed and published [@ijtiff].


### `autothresholdr`

```{r autothresholdr-downloads, echo=FALSE}
autothresholdr_downloads <- get_downloads("autothresholdr")
```

`autothresholdr` provides the _ImageJ_ [@ImageJ] _Auto Threshold_ plugin [@autothresholdr] functionality to R users. It gets `r autothresholdr_downloads$per_month` downloads per month which amounts to `r autothresholdr_downloads$total` since it was first released. 


### `detrendr`

```{r detrendr-downloads, echo=FALSE}
detrendr_downloads <- get_downloads("detrendr")
```

`detrendr` is an R package for detrending images (correcting for photobleaching). It provides all detrending algorithms mentioned in section \@ref(photobleaching-correction). The detrending is done in C++ in the background for speed but it is wrapped in an R package for ease of use. It gets `r detrendr_downloads$per_month` downloads per month which amounts to `r detrendr_downloads$total` since it was first released.



### `filesstrings`

```{r filesstrings-downloads, echo=FALSE}
filesstrings_downloads <- get_downloads("filesstrings")
```

`filesstrings` is an R package providing convenient functions for moving files, deleting directories, and a variety of string operations that facilitate manipulating file names and extracting information from strings. The motivation for making this package was to facilitate the use of file names for metadata. This is very common in microscopy, e.g. a filename like `well1_cell1_before_drug_addition.tif` is often seen. Using file names for metadata like this is a good idea, however if the naming or the extraction of data from these names is inconsistent, analysis becomes a nightmare and less reproducible. This package was peer reviewed and published [@filesstrings]. It gets `r filesstrings_downloads$per_month` downloads per month which amounts to `r filesstrings_downloads$total` since it was first released.



### `exampletestr`


```{definition}
_Unit testing_ is a software testing method by which individual units of source code, sets of one or more computer program modules together with associated control data, usage procedures, and operating procedures, are tested to determine whether they are fit for use.^[https://en.wikipedia.org/wiki/Unit_testing]
```

```{r exampletestr-downloads, echo=FALSE}
exampletestr_downloads <- get_downloads("exampletestr")
```

Unit testing is a tool to verify that software is performing as intended. It is a great way to discover bugs in software. `exampletestr` is an R package which makes it easier for R package developers to write unit tests for their packages. It helped me to eradicate many bugs in all of my packages. Interestingly, `exampletestr` was used to unit test and eradicate bugs in itself! This package was peer reviewed and published in 2017.[@exampletestr] It gets `r exampletestr_downloads$per_month` downloads per month which amounts to `r exampletestr_downloads$total` since it was first released.


