--- 
title: "Algorithms for the Correction of Photobleaching"
author: "Rory Nolan"
date: "University of Oxford"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib, papers.bib, webpages.bib, theses.bib]
biblio-style: apalike
link-citations: yes
fontsize: 12pt
geometry: margin=35mm
linkcolor: blue
citecolor: green
urlcolor: NavyBlue
toccolor: blue
linestretch: 2
description: "Rory Nolan's PhD thesis"
---


# Preface {-}

```{r load-pkgs, include=FALSE}
# The dev version of latex2exp is needed
pacman::p_load(tidyverse, forcats, magrittr, ijtiff, cranlogs, lubridate,
               curl, detrendr, nandb, filesstrings, knitr, latex2exp,
               janitor, RcppRoll, abind, brownded, here, readxl)

opts_chunk$set(comment = "#>", fig.asp = 0.6, 
               out.width = "100%", fig.align = "left",
               message = FALSE, warning = FALSE)

gg_color_hue <- function(n) {
  hues = seq(15, 375, length = n + 1)
  hcl(h = hues, l = 65, c = 100)[1:n]
}

move_to_groups_folder <- function() {
  groups_theses_path <- str_c("/Volumes/groups/cellular-imaging/",
                              "ReadingList/Theses/Rory")
  if (dir.exists(groups_theses_path)) {
    file.copy(here("_book", "phdthesis.pdf"), groups_theses_path)
    message("success")
  } else {
    message("failure")
  }
}
```


## Ways to read {-}

This thesis may be read on the web at https://rorynolan.github.io/phdthesis/. If you are reading this on the web now but would like a PDF version, click on the download symbol at the top left of the page (to the right of the __A__) and select PDF. 


## Apportion of credit {-}

For clarity I include the following reliable rules of thumb:

* Molecular biology was done by Maro Iliopoulou and Luis Alvarez.
* Imaging was done by Maro Iliopoulou, Luis Alvarez and Sergi Padilla-Parra.
* The idea that correction for bleaching was the crucial step for FFS analysis was formulated by Luis Alvarez, Sergi Padilla-Parra and I.
* I formulated the solutions for how to correctly correct for bleaching, i.e. the automatic parameter choice and the Robin Hood algorithm.
* I wrote all of the software and maintain all of it.
* All FFS analysis was performed using my software. The software was used to analyse data by Maro Iliopoulou, Luis Alvarez, Sergi Padilla Parra and I. 
* Structural modelling was done by Thomas Bowden and Yasunori Watanabe.
* On all papers where I am the first listed author, I wrote the paper, taking suggested amendments and augmentation from other listed authors. The NSMB paper [@HIVstoichiometry] was written by Sergi; I also made significant contributions to the writing of that manuscript but my main role in that project was in data analysis. 


## Publications {-}

I hereby list my publications. These can all be downloaded from https://github.com/rorynolan/phdthesis/tree/master/papers, where the naming convention is `JournalYEAR.pdf`.

#### First author {-}

* R. Nolan and S. Padilla-Parra. "filesstrings: An R package for file and
string manipulation". In: _Journal of Open Source Software_ 2.14 (2017).
* R. Nolan and S. Padilla-Parra. "exampletestr—An easy start to unit
testing R packages". In: _Wellcome Open Research_ 2 (2017).
* R. Nolan, L. Alvarez, J. Elegheert, et al. "nandb—number and brightness
in R with a novel automatic detrending algorithm". In: _Bioinformatics_ 33.21
(2017).
* R. Nolan, M. Iliopoulou, L. Alvarez, et al. "Detecting protein
aggregation and interactions in live cells: a guide to Number and
Brightness". In: _Methods_ (2017).
* R. Nolan and S. Padilla-Parra. "ijtiff: An R package providing TIFF I/O
for ImageJ users". In: _Journal of Open Source Software_ 3.23 (2018).
* R. Nolan, L. Alvarez, S. C. Griffiths, et al. “Calibration-Free In-Vitro
Quantification of Protein Homo-Oligomerization Using Commercial
Instrumentation and Free, Open Source Brightness Analysis Software”. In:
_Journal of Visualized Experiments_ 0.0 (2018).

#### Co-first author {-}

* M. Iliopoulou, R. Nolan, et al. "A dynamic three step
mechanism drives the HIV-1 pre-fusion reaction". In: _Nat. Struct. Mol. Biol._
0.0 (2018).

#### Other {-}

* D. M. Jones, L. A. Alvarez, R. Nolan, et al. "Dynamin-2 stabilizes the
HIV-1 fusion pore with a low oligomeric state". In: _Cell reports_ 18.2
(2017).
* G. M. Jakobsdottir, M. Iliopoulou, R. Nolan, et al. "On the whereabouts
of HIV-1 cellular entry and its fusion ports". In: _Trends in molecular
medicine_ (2017).
* Q. F. Wills, E. Mellado-Gomez, R. Nolan, et al. "The nature and nurture
of cell heterogeneity: accounting for macrophage gene-environment
interactions with single-cell RNA-Seq". In: _BMC genomics_ 18.1 (2017).


#### In preparation {-}

* The _Robin Hood_ algorithm (described in section \@ref(robin-hood-detrending)) will be submitted to a journal after the submission of this thesis but before the end of my PhD contract.


## Acronyms used in this thesis {-}

```{r acro, echo=FALSE}
read_excel(here("misc", "AcroMath.xlsx"), sheet = "Acro") %>% 
  arrange(Acronym) %>% 
  filter(!duplicated(Acronym)) %>% 
  kable()
```


## Mathematical symbols used in this thesis {-}

```{r math-symbols, echo=FALSE}
read_excel(here("misc", "AcroMath.xlsx"), sheet = "Math") %>% 
  arrange(Meaning) %>% 
  filter(!duplicated(Symbol)) %>%
  mutate(Symbol = str_c("$", Symbol, "$")) %>% 
  kable()
```