--- 
title: "Algorithms for the Correction of Photobleaching"
author: "Rory Nolan"
date: "University of Oxford"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib, papers.bib, webpages.bib, theses.bib]
biblio-style: apalike
link-citations: yes
fontsize: 12pt
geometry: margin=35mm
linkcolor: blue
citecolor: green
urlcolor: NavyBlue
toccolor: blue
description: "Rory Nolan's PhD thesis"
---


# Preface {-}

```{r load-pkgs, include=FALSE}
# The dev version of latex2exp is needed
pacman::p_load(tidyverse, forcats, magrittr, ijtiff, cranlogs, lubridate,
               curl, detrendr, nandb, filesstrings, knitr, latex2exp,
               janitor, RcppRoll, abind, brownded, here, readxl, DescTools,
               assertthat)

opts_chunk$set(comment = "#>", fig.asp = 0.6, 
               out.width = "100%", fig.align = "left",
               message = FALSE, warning = FALSE)

gg_color_hue <- function(n) {
  hues = seq(15, 375, length = n + 1)
  hcl(h = hues, l = 65, c = 100)[1:n]
}

move_to_groups_folder <- function() {
  groups_theses_path <- str_c("/Volumes/groups/cellular-imaging/",
                              "ReadingList/Theses/Rory")
  if (dir.exists(groups_theses_path)) {
    file.copy(here("_book", "phdthesis.pdf"), groups_theses_path)
    message("success")
  } else {
    message("failure")
  }
}
```


## Ways to read {-}

This thesis may be read on the web at https://rorynolan.github.io/phdthesis/. If you are reading this on the web now but would like a PDF version, click on the download symbol at the top left of the page (to the right of the __A__) and select PDF. 


## Apportion of credit {-}

For clarity, I include the following reliable rules of thumb:

* Molecular biology was done by Maro Iliopoulou and Luis Alvarez.
* Imaging was done by Maro Iliopoulou, Luis Alvarez and Sergi Padilla-Parra.
* The idea that correction for bleaching was the crucial step for FFS analysis was formulated by Luis Alvarez, Sergi Padilla-Parra and I.
* I formulated the solutions for how to correctly correct for bleaching, i.e. the automatic parameter choice and the Robin Hood algorithm.
* I wrote all of the software and maintain all of it.
* All FFS analysis was performed using my software. The software was used to analyse data by Maro Iliopoulou, Luis Alvarez, Sergi Padilla Parra and I. 
* Structural modelling was done by Thomas Bowden and Yasunori Watanabe.
* On all papers where I am the first listed author, I wrote the paper, taking suggested amendments and augmentation from other listed authors. The NSMB paper [@HIVstoichiometry] was written by Sergi; I also made significant contributions to the writing of that manuscript but my main role in that project was in data analysis. 


## Publications {-}

I hereby list my publications. These can all be downloaded from https://github.com/rorynolan/phdthesis/tree/master/papers, where the naming convention is `JournalYEAR.pdf`.

### First author {-}

* R. Nolan and S. Padilla-Parra. "filesstrings: An R package for file and
string manipulation". In: _Journal of Open Source Software_ 2.14 (2017).
* R. Nolan and S. Padilla-Parra. "exampletestr—An easy start to unit
testing R packages". In: _Wellcome Open Research_ 2 (2017).
* R. Nolan, L. Alvarez, J. Elegheert, et al. "nandb—number and brightness
in R with a novel automatic detrending algorithm". In: _Bioinformatics_ 33.21 (2017).
* R. Nolan, M. Iliopoulou, L. Alvarez, et al. "Detecting protein
aggregation and interactions in live cells: a guide to Number and
Brightness". In: _Methods_ (2017).
* R. Nolan and S. Padilla-Parra. "ijtiff: An R package providing TIFF I/O
for ImageJ users". In: _Journal of Open Source Software_ 3.23 (2018).
* R. Nolan, L. Alvarez, S. C. Griffiths, et al. “Calibration-Free In-Vitro
Quantification of Protein Homo-Oligomerization Using Commercial
Instrumentation and Free, Open Source Brightness Analysis Software”. In:
_Journal of Visualized Experiments_ 137 (2018).
* R. Nolan and S. Padilla-Parra. "Robin Hood: non-fitting, non-smoothing image detrending for bleaching correction". In: _BioRxiv_ (2019). 

### Co-first author {-}

* M. Iliopoulou, R. Nolan, et al. "A dynamic three step
mechanism drives the HIV-1 pre-fusion reaction". In: _Nat. Struct. Mol. Biol._
25.9 (2018).

### Other {-}

* D. M. Jones, L. A. Alvarez, R. Nolan, et al. "Dynamin-2 stabilizes the
HIV-1 fusion pore with a low oligomeric state". In: _Cell reports_ 18.2
(2017).
* G. M. Jakobsdottir, M. Iliopoulou, R. Nolan, et al. "On the whereabouts
of HIV-1 cellular entry and its fusion ports". In: _Trends in molecular
medicine_ (2017).
* Q. F. Wills, E. Mellado-Gomez, R. Nolan, et al. "The nature and nurture
of cell heterogeneity: accounting for macrophage gene-environment
interactions with single-cell RNA-Seq". In: _BMC genomics_ 18.1 (2017).


## Acronyms used in this thesis {-}

```{r acro, echo=FALSE}
read_excel(here("misc", "AcroMath.xlsx"), sheet = "Acro") %>% 
  arrange(Acronym) %>% 
  filter(!duplicated(Acronym)) %>% 
  kable(longtable = TRUE)
```


## Mathematical symbols used in this thesis {-}

```{r math-symbols, echo=FALSE}
read_excel(here("misc", "AcroMath.xlsx"), sheet = "Math") %>% 
  arrange(Meaning) %>% 
  filter(!duplicated(Symbol)) %>%
  mutate(Symbol = str_c("$", Symbol, "$")) %>% 
  kable(escape = FALSE, longtable = TRUE)
```


## Acknowledgements {-}

Thanks to my parents Kate and Dave who were good enough to house me rent-free for 18 years. They encouraged me academically after it became clear that I was not the next Kevin Kilbane. Thanks to my wife Naomi who puts up with me now that my parents have had enough of me. Thanks to my brother Brendan who taught me (perhaps wrongly) that maths is cool.

Thanks to my supervisor Sergi Padilla-Parra who had many good ideas of what to study, for his intelligent input and generosity with time. Moreover, thanks to him for emphasising that it's possible to work too hard. It's largely thanks to his attitude that my time in Oxford was so enjoyable. 

Thanks to all of my lab mates: Dan, Keith, Xenia, Raquel, Luis, Margarita, Marina, Maro, Marina, Maria, Chad and Irene; it was interesting and fun to spend time with you all. I'll look back upon my time in the lab fondly, I hope you can say the same. 

Thanks to my friends Kathrin and Zammy from my PhD programme; we shared the journey to becoming doctors and come out of the other end with lifelong friendships as well as new titles.

Thanks to my college friends Bas, Jessica, Francis, Sarah, Andy, Frankie, Jonny, Suze, Walid, Sophia, Martin, Max, Maj, Nirmalie, Luiza, LD and many more. It was a privilege to have so many good friends at once.

There are plenty more people I should thank, but I'm tired so I'm going to stop now.